---
title: ''
author: ''
date: ''
output:
  word_document:
    reference_docx: style.1.docx
  html_document:
    df_print: paged
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 5 * 1.67, fig.height = 5)

  load("data.RData")
  data_cfa <- data; rm(data) # Data set with no missings for CFA items
  
  load("data_full.RData")

  source("scripts/functions.R")

  library(pander)
  library(ggrepel)
  library(tidyverse)
  library(viridis)
  library(likert)
  library(rms)
  library(Hmisc)
  library(broom)
  library(lavaan)
  library(ggbeeswarm)
  library(gridExtra)
  library(grid)
  library(knitr)
  
  d <- datadist(data)
  options(datadist = "d")
  
```


```{r plot_function}

  likert_data <- function(data, q_stub, q_labs){
    
    q_levs <- names(select(data, starts_with(q_stub)))
    
    likert_labs <- c("Strongly disagree",	"Disagree",
                     "Neither agree nor disagree", "Agree",	"Strongly agree")
    
# Reshape data to long, tack on questions and response labels, 
# then go back to wide 
    df <- data %>%
      gather(question, response, starts_with(q_stub)) %>%
      mutate(question = factor(question, levels = q_levs, labels = q_labs), 
             response = factor(response, levels = likert_labs)) %>%
      spread(question, response)

# df <- df[complete.cases(df), ] # Keep just the complete cases for that 
# subset of Qs
    
    class(df) <- class(df)[3] # likert can't handle the tibble
    df <- df[order(names(df))]
    df$all <- "All"
    df$all <- factor(df$all, levels = c("All", "Other"))
    return(df)
  }

# Plot the data
  
    likert_plot_group <- function(data, start, end, group, ...){
      plot(likert(data[start:end], grouping = data[[group]]), 
         col = viridis(5), panel.strip.color = "white", wrap = 100) +
      guides(fill = guide_legend(title = "", nrow = 1, byrow = TRUE)) +
      theme_minimal() +
      ylab("") +
      theme(panel.grid = element_blank(), 
            legend.position = "bottom", 
            legend.key.size = unit(0.5,"line"))
  }

```

# Respondent characteristics

These are based on the full data set (n = `r nrow(data)`) with no observations dropped for missing data.

```{r table1_data}

  descript <- select(data, 
                     sex, age, age_groups, yearsonregister, years_groups, 
                     enrolledonscheme, division, status,
                     hours, role, servicemodel, 
                     country, country_groups, county_dublin, passport_ireland)

```

```{r table1_describe}

  data_frame(Variable       = name.1(descript),
             N              = n.miss(descript),
             "Mean SD"      = summary.1(descript),
             "Median [IQR]" = med.iqr(descript),
             "(Min, Max)"   = min.max(descript)) %>% knitr::kable()
  
```

```{r dfsummary_table1, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

  print(summarytools::dfSummary(descript, style = "grid", plain.ascii = FALSE), 
    method = "render")

```

# Survey items and intent

These are based on the full data set (n = `r nrow(data)`) with no observations dropped for missing data.

## F1: Items 1-7 & 21: Attitudes to Maintenance of Professional Competence

```{r dfsummary_f1, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

  df <- select(data, starts_with("mpc_"), starts_with("part_"), agree_21_tickbox)

  print(summarytools::dfSummary(df, style = "grid", plain.ascii = FALSE), 
        method = "render")

```

Do you argree with the following statements about the MPC?
```{r mpc_likert}

  labs <- c(
    "01. Reassures patients and the public that doctors are fit to practice",
    "02. Encourages doctors to continually learn and keep up to date",
    "03. Raises the standard of practice of all doctors "
  )

  mpc <- likert_data(data, "mpc_", labs) 
  likert_plot_group(mpc, 1, length(labs), "all") +
    theme(axis.text.y = element_blank())

```

By intent to comply (yes/no)
```{r mpc_likert_intends}

  likert_plot_group(mpc, 1, length(labs), "binary_intention") 

```

Do you argree with the following statements about personal impact of participation?
```{r part_likert}

  labs <- c(
    "4. Encourages me to reflect more on my professional development",
    "5. Encourages me to participate in more educational activities", 
    "6. Has resulted in changes in my practice",
    "7. Provides benefits that are worth the time, effort and expense involved" 
  )
 
  part <- likert_data(data, "part_", labs) 
  likert_plot_group(part, 1, length(labs), "all") +
    theme(axis.text.y = element_blank())
  
```

By intent to comply (yes/no)
```{r part_likert_intends}

  likert_plot_group(part, 1, length(labs), "binary_intention") 

```

How do all of these items relate to intention?
```{r beliefs_intends_bar_plot}

  df <- select(
    data, starts_with("mpc_"), starts_with("part_"), agree_21_tickbox, intends
    ) %>%
    gather(var, val, -intends) %>%
    mutate(val = factor(val, levels = levels(factor(val))[c(4, 1, 3, 2, 5)])) %>%
    mutate(var = gsub("mpc_", "", var)) %>%
    mutate(var = gsub("part_", "", var)) %>%
    mutate(var = gsub("agree_", "", var)) 


  ggplot(df, aes(x = val, fill = intends)) +
    geom_bar(position = "fill") +
    scale_fill_viridis("", discrete = TRUE, 
                       guide = guide_legend(reverse = TRUE)) +
    facet_wrap(~var, nrow = 2) +
    ylab("Proportion") +
    xlab("") +
    coord_flip() +
    theme_minimal() +
    theme(legend.position = "bottom", 
          axis.text.x = element_text(size = 8, angle = 90, hjust = 1),
          panel.grid = element_blank(), 
          strip.text = element_text(size = 8))
  
  # +
  #   theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

```{r}

  levs <- c("Disagree", "Neither agree nor disagree", "Agree",	
            "Strongly agree")

  orm_models <- function(data, var_names, ...){
    options(contrasts = c("contr.treatment", "contr.treatment"))
    model_frame <- data_frame()
    for(i in var_names){
      form <- as.formula(paste0("intends ~ ", i))
      m <- orm(form, data = data)
      p <- anova(m)
      model_frame <- bind_rows(
        data_frame(
          quest = i,
          var = gsub(paste0(i, "="), "", 
                     names(m$coeff)[!grepl("y>=", names(m$coeff))]), 
          logodds = m$coeff[!grepl("y>=", names(m$coeff))], 
          se = sqrt(diag(m$var)[!grepl("y>=", names(diag(m$var)))]), 
          or = exp(logodds),
          ul = exp(logodds + 1.96*se),
          ll = exp(logodds - 1.96*se), 
          p_cat = cut(p[i, ][3], c(0, 0.001, 0.01, 0.05, 1), 
                          include.lowest = TRUE)
        ), 
        model_frame
      ) %>%
       mutate(var = factor(var, levels = levs)) 
    }
    return(model_frame)
  }

# options(contrasts = c("contr.treatment", "contr.poly")) # Normal settings


```

Proportional odds models for intent regressed on each item
```{r}

  var_names <- names(select(data, starts_with("mpc_"), starts_with("part_"),
                            agree_21_tickbox))

  df <- orm_models(data, var_names)

  ggplot(df, aes(x = var, y = or, ymax = ul, ymin = ll, color = p_cat)) +
    geom_pointrange() +
    geom_hline(yintercept = 1, linetype = "dashed") +
    theme_minimal() +
    facet_wrap(~quest) +
    ylab("OR (95% CI)") +
    xlab("") +
    scale_color_viridis("LRT p-value", discrete = TRUE) +
    coord_flip() +
    theme(strip.text = element_text(size = 8))
  
```

## F2: Items 8-15 & 26: Barriers to Engagement with Maintenance of Professional Competence

```{r dfsummary_f2, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

  df <- select(data, starts_with("barrier_"), agree_26_pcsusedagainstme)

  print(summarytools::dfSummary(df, style = "grid", plain.ascii = FALSE), 
        method = "render")
```

Please indicate your agreement with these statements about BARRIERS to your own engagement with Maintenance of Professional Competence in Ireland
```{r barrier_likert_1}

  labs <- c(
    "08. I do not understand what I am required to do for Maintenance of Professional Competence",
    "09. Lack of protected time makes it difficult to undertake activities to earn points",
    "10. The expense of the annual Professional Competence Scheme fee is a barrier", 
    "11. The expense of Continuing Professional Development(CPD) activities is a barrier", 
    "12. The expense of paying a locum to allow me to attend CPD activities is a barrier", 
    "13. The requirement to record my learning activities through an online platform has been a barrier", 
    "14. Lack of audit skills has been a barrier", 
    "15. Difficulty identifying a suitable audit topic has been a barrier"
  )
 
  barrier <- likert_data(data, "barrier_", labs) 
  likert_plot_group(barrier, 1, 4, "all") +
    theme(axis.text.y = element_blank())
  
```

```{r barrier_likert_2}

  likert_plot_group(barrier, 5, 8, "all") +
    theme(axis.text.y = element_blank())

```

By intent to comply (yes/no)

```{r barrier_likert_1_intends}

  likert_plot_group(barrier, 1, 4, "binary_intention") 

```

```{r barrier_likert_2_intends}

  likert_plot_group(barrier, 5, 8, "binary_intention") 

```

How do all of these items relate to intention?
```{r}

  df <- select(
    data, starts_with("barrier_"), agree_26_pcsusedagainstme, intends
    ) %>%
    gather(var, val, -intends) %>%
    mutate(val = factor(val, levels = levels(factor(val))[c(4, 1, 3, 2, 5)])) %>%
    mutate(var = gsub("barrier_", "", var)) %>%
    mutate(var = gsub("engage_", "", var)) %>%
    mutate(var = gsub("agree_", "", var)) %>%
    filter(!is.na(val))


  ggplot(df, aes(x = val, fill = intends)) +
    geom_bar(position = "fill") +
    scale_fill_viridis("", discrete = TRUE, 
                       guide = guide_legend(reverse = TRUE)) +
    facet_wrap(~var) +
    ylab("Proportion") +
    xlab("") +
    coord_flip() +
    theme_minimal() +
    theme(legend.position = "bottom", 
          axis.text.x = element_text(size = 8, angle = 90, hjust = 1),
          panel.grid = element_blank(), 
          strip.text = element_text(size = 8))

```

Proportional odds models for intent regressed on each item
```{r}

  var_names <- names(select(data, starts_with("barrier_"), 
                            agree_26_pcsusedagainstme))

  df <- orm_models(data, var_names)

  ggplot(df, aes(x = var, y = or, ymax = ul, ymin = ll, color = p_cat)) +
    geom_pointrange() +
    geom_hline(yintercept = 1, linetype = "dashed") +
    theme_minimal() +
    facet_wrap(~quest) +
    ylab("OR (95% CI)") +
    xlab("") +
    scale_color_viridis("LRT p-value", discrete = TRUE) +
    coord_flip() +
    theme(strip.text = element_text(size = 8))
  
```


## F3: Items 17-20: Facilitators of Engagement with Maintenance of Professional Competence
```{r dfsummary_f3, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

  df <- select(data, starts_with("engage_"))

  print(summarytools::dfSummary(df, style = "grid", plain.ascii = FALSE), 
          method = "render")
```

Please indicate your agreement with the following statements about factors which SUPPORT your own engagement with Maintenance of Professional Competence in Ireland
```{r engage_likert}

  labs <- c(
    "17. The CPD activities I need to address gaps in my knowledge and practice are currently available",
    "18. I can access high quality CPD activities",
    "19. My Professional Competence Scheme provides enough flexible ways to meet requirements",
    "20. My Professional Competence Scheme provides useful information to help me to meet requirements"
  )
 
  engage <- likert_data(data, "engage_", labs) 
  likert_plot_group(engage, 1, length(labs), "all") +
    theme(axis.text.y = element_blank())
  
```

By intent to comply (yes/no)
```{r engage_likert_intends}

  likert_plot_group(engage, 1, length(labs), "binary_intention") 

```

How do all of these items relate to intention?
```{r}

  df <- select(
    data, starts_with("engage_"), intends
    ) %>%
    gather(var, val, -intends) %>%
    mutate(val = factor(val, levels = levels(factor(val))[c(4, 1, 3, 2, 5)])) %>%
    mutate(var = gsub("engage_", "", var)) %>%
    mutate(var = gsub("agree_", "", var)) %>%
    filter(!is.na(val))


  ggplot(df, aes(x = val, fill = intends)) +
    geom_bar(position = "fill") +
    scale_fill_viridis("", discrete = TRUE, 
                       guide = guide_legend(reverse = TRUE)) +
    facet_wrap(~var) +
    ylab("Proportion") +
    xlab("") +
    coord_flip() +
    theme_minimal() +
    theme(legend.position = "bottom", 
          axis.text.x = element_text(size = 8, angle = 90, hjust = 1),
          panel.grid = element_blank(), 
          strip.text = element_text(size = 8))

```

Proportional odds models for intent regressed on each item
```{r}

  var_names <- names(select(data, starts_with("engage_")))

  df <- orm_models(data, var_names)

  ggplot(df, aes(x = var, y = or, ymax = ul, ymin = ll, color = p_cat)) +
    geom_pointrange() +
    geom_hline(yintercept = 1, linetype = "dashed") +
    theme_minimal() +
    facet_wrap(~quest) +
    ylab("OR (95% CI)") +
    xlab("") +
    scale_color_viridis("LRT p-value", discrete = TRUE) +
    coord_flip() +
    theme(strip.text = element_text(size = 8))
  
```


## F4: Items 27-29: Social Norms relating to Maintenance of Professional Competence

```{r dfsummary_f4, eval = knitr::opts_knit$get("rmarkdown.pandoc.to") == "html"}

  df <- select(data, agree_27_importantforpts:agree_29_riskremoval)

  print(summarytools::dfSummary(df, style = "grid", plain.ascii = FALSE), 
          method = "render")
```

```{r social_likert}

  labs <- c(
    "21. Maintenance of Professional Competence is a tick box exercise",
    "22. I match my CPD activities to gaps in my knowledge and practice",
    "23. I would welcome the opportunity to use patient feedback to demonstrate my professional competence",
    "24. I would welcome the opportunity to use feedback from colleagues to demonstrate my professional competence",
    "25. I would welcome the opportunity to submit a quality improvement initiative rather than an audit",
    "26. I am concerned that information I provide to my Professional Competence Scheme about my knowledge and practice could be used against me if my competence was in question",
    "27. It is important to my patients that I meet the requirements for Professional Competence",
    "28. It is important to my colleagues that I meet the requirements for Professional Competence",
    "29. Doctors who do not participate in Maintenance of Competence risk being removed from the register",
    "30. I am confident that I can fulfil the requirements for Maintenance of Competence"
  )
 
  social <- likert_data(data, "agree_", labs) 
  likert_plot_group(social, 7, 9, "all") +
    theme(axis.text.y = element_blank())
  
```

Intends to comply
```{r social_likert_intends}

  likert_plot_group(social, 7, 9, "binary_intention") 

```

How do all of these items relate to intention?
```{r social_intends_bar_plot}

  df <- select(data, agree_27_importantforpts:agree_29_riskremoval, intends) %>%
    gather(var, val, -intends) %>%
    mutate(val = factor(val, levels = levels(factor(val))[c(4, 1, 3, 2, 5)])) %>%
    mutate(var = gsub("agree_", "", var)) %>%
    filter(!is.na(val))


  ggplot(df, aes(x = val, fill = intends)) +
    geom_bar(position = "fill") +
    scale_fill_viridis("", discrete = TRUE, 
                       guide = guide_legend(reverse = TRUE)) +
    facet_wrap(~var) +
    ylab("Proportion") +
    xlab("") +
    coord_flip() +
    theme_minimal() +
    theme(legend.position = "bottom", 
          axis.text.x = element_text(size = 8, angle = 90, hjust = 1),
          panel.grid = element_blank(), 
          strip.text = element_text(size = 8))

```

Proportional odds models for intent regressed on each item
```{r}

  var_names <- names(select(data, agree_27_importantforpts:agree_29_riskremoval))

  df <- orm_models(data, var_names)

  ggplot(df, aes(x = var, y = or, ymax = ul, ymin = ll, color = p_cat)) +
    geom_pointrange() +
    geom_hline(yintercept = 1, linetype = "dashed") +
    theme_minimal() +
    facet_wrap(~quest) +
    ylab("OR (95% CI)") +
    xlab("") +
    scale_color_viridis("LRT p-value", discrete = TRUE) +
    coord_flip() +
    theme(strip.text = element_text(size = 8))
  
```

# Full CFA

These are based on the reduced data set (n = `r nrow(data_cfa)`) with observations dropped for missing values for measurements used in the CFA.

```{r cfa_full}

  full <- '
    Beliefs_f1 =~ mpc_01_reassurespublic + mpc_02_encouragesdoctors + 
      mpc_03_raisesstandards + part_04_encouragesmereflect + 
      part_05_encouragesmeeducation + part_06_resultchangeinpractice +
      part_07_worthtimeeffortexpense + agree_21_tickbox
      
    Barriers_f2 =~ barrier_08_dontunderstandreq + barrier_09_lackprottime + 
      barrier_10_pcsfeeabarrier + barrier_11_cpdexpenseabarrier + 
      barrier_13_onlineplatformabarrier + 
      barrier_14_lackauditskillsabarrier + barrier_15_topicabarrier + 
      agree_26_pcsusedagainstme
      
    Engage_f3 =~ engage_17_cpdaddressesgaps + engage_18_cpdaccessible + 
      engage_19_pcsflexible + engage_20_pcsinfosufficient
      
    Social_f4 =~ agree_27_importantforpts + agree_28_importantforcolleagues + 
      agree_29_riskremoval  
  '
  full_m <- cfa(full, data = data_cfa)
# summary(full_m, standardized = TRUE, rsquare = TRUE, ci = TRUE,
#         fit.measures = TRUE)

  x <- predict(full_m)

#  data$beliefs <- as.numeric(predict(beliefs_m))
  
  data_cfa$beliefs_f1  <- x[, 1]
  data_cfa$barriers_f2 <- x[, 2]
  data_cfa$engage_f3   <- x[, 3]
  data_cfa$social_f4   <- x[, 4]


```

```{r full_cfa_density}

  labs <- c("Barriers (F2)", "Beliefs (F1)", "Engage (F3)", "Social (F4)")

  select(data_cfa, beliefs_f1:social_f4, intends) %>%
    gather(factor, value, -intends) %>%
    mutate(factor = factor(factor, labels = labs)) %>%
    mutate(factor = factor(
      factor, levels = levels(factor(factor))[c(2, 1, 3, 4)]
      )) %>%
  ggplot(aes(x = value, fill = intends)) +
    geom_density(alpha = 0.4) +
    geom_density(fill = "white", alpha = 0, size = 1, linetype = "dashed") +
    theme_minimal() +
    facet_wrap(~factor) + 
    ylab("Density") +
    xlab("Factor score") +
    scale_fill_viridis("", discrete = TRUE)

```


```{r factor_histogram_function}

  bar_factor <- function(variable, label, ...){

  g1 <- ggplot(data_cfa, aes(x = get(variable), fill = intends)) +
    geom_histogram() +
    theme_minimal() +
    ylab("Number of respondents") +
    xlab("") +
    scale_fill_viridis(guide = FALSE, discrete = TRUE)

  g2 <- ggplot(data_cfa, aes(x = get(variable), fill = intends)) +
      geom_histogram(position = "fill") +
      theme_minimal() +
      ylab("Proportion of respondents") +
      xlab(label) +
      scale_fill_viridis("", discrete = TRUE) +
      theme(legend.position = "bottom")

  return(grid.arrange(g1, g2, ncol = 1))
  
  }

```

```{r }
 
  bar_factor("beliefs_f1", "Beliefs (F1) score")  

```

```{r }
 
  bar_factor("barriers_f2", "Barriers (F2) score")  

```

```{r }
 
  bar_factor("engage_f3", "Engage (F3) score")  

```

```{r }
 
  bar_factor("social_f4", "Social (F4) score")  

```

```{r}
  parameterEstimates(full_m, standardized = TRUE) %>% 
    filter(op == "=~") %>% 
    select("Latent Factor" = lhs, Indicator = rhs, B = est, SE = se, Z = z,
           'p-value' = pvalue, Beta = std.all) %>% 
    kable(digits = 3, format = "pandoc", caption = "Factor Loadings")
```


```{r}
  parameterEstimates(full_m, standardized = TRUE) %>% 
    filter(op == "~~", 
           lhs %in% c("Beliefs_f1", "Barriers_f2", "Barriers_f2"), 
           !is.na(pvalue)) %>% 
    select('Factor 1' = lhs, 
           'Factor 2' = rhs, 
           Correlation = est, 
           "P value" = pvalue) %>% 
    kable(digits = 3, format = "pandoc",
          caption = "Latent Factor Correlations")
```


```{r}
  data_frame(
    Measure = names(fitMeasures(full_m)), 
    Value = fitMeasures(full_m)
    ) %>% 
  filter(Measure %in% c("chisq", "df", "pvalue", "cfi", "tli", "rmsea",
                        "rmsea.pvalue")) %>% 
  kable(digits = 3, format = "pandoc", caption = "Model fit")
```

# Proportional odds models for intends

These are based on the reduced data set (n = `r nrow(data_cfa)`) with observations dropped for missing values for measurements used in the CFA (as factor scores are used as predictors in these models).

```{r}
# gender, country_groups, division, role, service model, passport country 

  d <- datadist(data_cfa)
  options(datadist = "d")

  m <- orm(intends ~ rcs(beliefs_f1, 5) + rcs(barriers_f2, 5) + 
             rcs(engage_f3, 5) + rcs(social_f4, 5) + 
             country_groups + sex + division +
             role + servicemodel + passport_ireland, 
           data = data_cfa)
  df <- data_frame(
          var = names(m$coeff)[!grepl("y>=", names(m$coeff))], 
          level = names(m$coeff)[!grepl("y>=", names(m$coeff))], 
          logodds = m$coeff[!grepl("y>=", names(m$coeff))], 
          se = sqrt(diag(m$var)[!grepl("y>=", names(diag(m$var)))]), 
          or = exp(logodds),
          ul = exp(logodds + 1.96*se),
          ll = exp(logodds - 1.96*se)
        )
  
  df$var <- gsub("=.*$", "", df$var) # Keep just the variable names
  df$level <- gsub(".*=", "", df$level) # Keep just the variable levels
  
  k <- 1
  for(i in df$var){
    if(i %in% names(data)){
      if(is.factor(data[[i]])){
        df$var[k] <- paste0(
          i, " (ref = ", levels(data[[i]])[1], ")"
        )
      }
      else(df$var[k] <- df$var[k])
    }
    else(df$var[k] <- df$var[k])
    k <- k + 1
  }
  
```

```{r}

  knitr::kable(signif(anova(m), 2))

```

```{r}
  ggplot(Predict(m, beliefs_f1)) + theme_minimal()
```

```{r}
  ggplot(Predict(m, barriers_f2)) + theme_minimal()
```

```{r}
  ggplot(Predict(m, engage_f3)) + theme_minimal()
```

```{r}
  ggplot(Predict(m, social_f4)) + theme_minimal()
```


```{r}

  or_plot <- function(data, ...){
    g <- ggplot(data, 
           aes(x = level, y = or, ymax = ul, ymin = ll, color = var)) +
      geom_pointrange() +
      geom_hline(yintercept = 1, linetype = "dashed") +
      theme_minimal() +
      ylab("OR (95% CI)") +
      xlab("") +
      facet_wrap(~var, scales = "free_y", ncol = 1) +
      coord_flip() +
      scale_color_viridis(guide = FALSE, discrete = TRUE, end = 0.8) +
      theme(axis.text.x = element_text(size = 8))
  
    return(g)
  }

  or_plot(
    filter(df[17:nrow(df), ], var == "role (ref = Community Health Doctor)")
  )

```

```{r}
  or_plot(
    filter(df[17:nrow(df), ], var != "role (ref = Community Health Doctor)")
  )
```


# Proportional odds models for confidence

These are based on the reduced data set (n = `r nrow(data_cfa)`) with observations dropped for missing values for measurements used in the CFA (as factor scores are used as predictors in these models).

```{r}
# gender, country_groups, division, role, service model, passport country 

  d <- datadist(data_cfa)
  options(datadist = "d")

  m <- orm(agree_30_confidencefulfillreq ~ rcs(beliefs_f1, 5) + 
             rcs(barriers_f2, 5) + 
             rcs(engage_f3, 5) + rcs(social_f4, 5) + 
             country_groups + sex + division +
             role + servicemodel + passport_ireland, 
           data = data_cfa)
  df <- data_frame(
          var = names(m$coeff)[!grepl("y>=", names(m$coeff))], 
          level = names(m$coeff)[!grepl("y>=", names(m$coeff))], 
          logodds = m$coeff[!grepl("y>=", names(m$coeff))], 
          se = sqrt(diag(m$var)[!grepl("y>=", names(diag(m$var)))]), 
          or = exp(logodds),
          ul = exp(logodds + 1.96*se),
          ll = exp(logodds - 1.96*se)
        )
  
  df$var <- gsub("=.*$", "", df$var) # Keep just the variable names
  df$level <- gsub(".*=", "", df$level) # Keep just the variable levels
  
  k <- 1
  for(i in df$var){
    if(i %in% names(data)){
      if(is.factor(data[[i]])){
        df$var[k] <- paste0(
          i, " (ref = ", levels(data[[i]])[1], ")"
        )
      }
      else(df$var[k] <- df$var[k])
    }
    else(df$var[k] <- df$var[k])
    k <- k + 1
  }
  
```

```{r}

  knitr::kable(signif(anova(m), 2))

```

```{r}
  ggplot(Predict(m, beliefs_f1)) + theme_minimal()
```

```{r}
  ggplot(Predict(m, barriers_f2)) + theme_minimal()
```

```{r}
  ggplot(Predict(m, engage_f3)) + theme_minimal()
```

```{r}
  ggplot(Predict(m, social_f4)) + theme_minimal()
```


```{r}

  or_plot(
    filter(df[17:nrow(df), ], var == "role (ref = Community Health Doctor)")
  )

```

```{r}
  or_plot(
    filter(df[17:nrow(df), ], var != "role (ref = Community Health Doctor)")
  )
```

# The relationship between gender, country_groups, division and questionnaire responses, using the binary responses. 

These are based on the full data set (n = `r nrow(data)`) with no observations dropped for missing data.

## Sex

```{r}

  select(data, sex, starts_with("binary")) %>%
    gather(var, val, starts_with("binary")) %>%
    mutate(var = gsub("binary_", "", var)) %>%

  ggplot(aes(x = sex, fill = val)) +
    geom_bar(position = "fill") +
    facet_wrap(~var) + 
    ylab("Proportion") +
    scale_fill_viridis("", discrete = TRUE, end = 0.5, na.value = "grey50") +
    theme_minimal() +
    theme(strip.text = element_text(size = 8))

```

```{r}

  df <- data_frame()
  for(i in names(select(data, starts_with("binary_")))){
    
    test <- chisq.test(data[["sex"]], data[[i]])
    df <- bind_rows(
      df, 
      data_frame(var = i, 
                 p = signif(test$p.value, 3))
    )
  }

  df <- df[order(df$p), ]

  df$m    <- nrow(df)
  df$i    <- c(1:nrow(df))
  df$q    <- 0.05
  df$fdrp <- with(df, i / m * q)
  df$sig  <- df$p <= df$fdrp
  
  kable(df)
  
```

## Division

```{r}

  select(data, division, starts_with("binary")) %>%
    gather(var, val, starts_with("binary")) %>%
    mutate(var = gsub("binary_", "", var)) %>%

  ggplot(aes(x = division, fill = val)) +
    geom_bar(position = "fill") +
    facet_wrap(~var) + 
    ylab("Proportion") +
    scale_fill_viridis("", discrete = TRUE, end = 0.5, na.value = "grey50") +
    theme_minimal() +
    theme(strip.text = element_text(size = 8), 
          axis.text.x = element_text(size = 8, angle = 90, hjust = 1))

```

```{r}

  df <- data_frame()
  for(i in names(select(data, starts_with("binary_")))){
    
    test <- chisq.test(data[["division"]], data[[i]])
    df <- bind_rows(
      df, 
      data_frame(var = i, 
                 p = signif(test$p.value, 3))
    )
  }

  df <- df[order(df$p), ]

  df$m    <- nrow(df)
  df$i    <- c(1:nrow(df))
  df$q    <- 0.05
  df$fdrp <- with(df, i / m * q)
  df$sig  <- df$p <= df$fdrp
  
  kable(df)
  
```

## Country groups

```{r}

  select(data, country_groups, starts_with("binary")) %>%
    gather(var, val, starts_with("binary")) %>%
    mutate(var = gsub("binary_", "", var)) %>%

  ggplot(aes(x = country_groups, fill = val)) +
    geom_bar(position = "fill") +
    facet_wrap(~var) + 
    ylab("Proportion") +
    scale_fill_viridis("", discrete = TRUE, end = 0.5, na.value = "grey50") +
    theme_minimal() +
    theme(strip.text = element_text(size = 8), 
          axis.text.x = element_text(size = 8, angle = 90, hjust = 1))

```

```{r}

  df <- data_frame()
  for(i in names(select(data, starts_with("binary_")))){
    
    test <- chisq.test(data[["country_groups"]], data[[i]])
    df <- bind_rows(
      df, 
      data_frame(var = i, 
                 p = signif(test$p.value, 3))
    )
  }

  df <- df[order(df$p), ]

  df$m    <- nrow(df)
  df$i    <- c(1:nrow(df))
  df$q    <- 0.05
  df$fdrp <- with(df, i / m * q)
  df$sig  <- df$p <= df$fdrp
  
  kable(df)
  
```




```{r}
# Ok, this is weird. If you plot the new factor scores, it shows a strong
# pattern in the data when orderd as they are. (goes away if you reorder by ID)

  # data$weird_row <- 1:nrow(data)
  # 
  # ggplot(data, aes(y = beliefs_f1, x = weird_row)) +
  #   geom_point() +
  #   xlab("Original sorting") +
  #   ylab("Beliefs (F1) CFA score") +
  #   theme_minimal()
  
# for(i in names(data)){
#   ggplot(data, aes(y = beliefs, x = weird_row, color = get(i))) +
#   geom_point() +
#   ggtitle(i)
#   
#   ggsave(paste0("plots/", i, ".png"))
# }

```


```{r}
# Looked at the plots and get perfect discrimination by these three variables

# table(data$binary_pcsfeeabarrier)
# table(data$binarystandards)
# table(data$binaryworthit)
  
  # ggplot(
  #   data, 
  #     aes(
  #       y = beliefs, x = weird_row, color = interaction(
  #         binary_pcsfeeabarrier, 
  #         binarystandards,                                                                 
  #         binaryworthit
  #         )
  #       )
  #   ) +
  #   geom_point() +
  #   scale_color_brewer("Fee, Stdrds, Worth", palette = "Set1") +
  #   theme_minimal() +
  #   theme(legend.position = "bottom") +
  #   xlab("Original sorting") +
  #   ylab("Beliefs (F1) factor score")
  
# standards and worthit are binary version of 2 of the likert scale indicators
# included in the belief model. So in the plot below, the first 4 bands are all
# No on pcsfeesabarrier, and the second 4 are Yes. Then, for each quartet, you
# get the same pattern with respect to the other 2: No-No, No-Yes, Yes-No,
# Yes-Yes.   
  
# Conclusion - is it just a conicidence that they were sorted this way, on 
# variables that happened to be included in the CFA?

```
